Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-07-04 review_article.Rmd
consider urbanisation

<!-- psychology -->
The familiar state shapes help viewers to visually infer spatial relationships, and hence intuitive to read [@CIBMUK]. However, the different sizes of administrative areas can lead viewers to place more attention on the shades of the largest areas. The inferences derived, and the hypotheses developed can suffer from a large area "bias". <!--This technique has been seen as a 'trigger for questions' which drives research of spatial distributions of diseases.  @MACM also recognise the intuition that can be derived from choropleths with the critique that they must be 'validated by rigorous statistical analyses.' -->

@@

@CPISACA
The potential audience for the results of a spatial analysis of health data is no longer limited to scientists but now also includes the public, policymakers, the media, and a host of others.

<!-- Usage and availability -->
@DMAHP cites Cruickshank's (1947) discussion of using visuals as 'formal statistical assessment of the spatial pattern' as a major advancement.
@CD considers cartographic data analysis in practice. Presenting a clear guide for preparing cartograms for use with both qualitative and quantitative information.
 The authors recognise that the creation of cartograms was largely the work of professional cartographers until the innovation of geographical information systems that welcomed map users as map creators. These systems are utilised depending on ‘the effectiveness, efficiency, and satisfaction of the map products (Nielsen 1994)’.

Using the recognisable geography, that is familiar, helps communicate the information.
-->

@@

Choropleths can inhibit visual inference when presenting human related statistics as the display may draw attention from the 'potentially more important results in the more populous communities' [@SE].

@@

Clear examples of:
White paper example for published Atlases
-methods they use

@@

@SAMGIS suggests it is the "investigators' objectives" that drive the "representation of diseases on maps". There will be situations like infectious diseases that require choropleth methods

@@

@@

Choropleth Maps, relationship between regions and spatial location. Able to represent all the occurrences within areas more cohesively, as total counts, or colours.

Urbanisation pushed people closer together, in workplaces and in homes.

>>>>

<!-- psychology -->
Utilising the familiar state shapes can make a map intuitive to read [@CIBMUK], and allow viewers to visually infer the spatial relationships in the data. 
The familiarity of the geography is a worthy consideration when presenting results of spatial analysis. Just as geographers are no longer the only creators of maps, @CPISACA suggests the audience of spatial health data analysis has extended beyond researchers to the public, policymakers and the media.
However, while they can be recognisable shapes, the different sizes of administrative areas can lead viewers to give more attention to the shades of the largest areas. Choropleths can inhibit visual inference when presenting human related statistics as the display may draw attention from the 'potentially more important results in the more populous communities' [@SE].

<!--
Urbanisation has pushed people closer together,
-in workplaces and in homes. 
-this issue is not with the size of the administrative areas,
- the increasing urbanisation is contributing to the changing density of population
-->

@@

<!-- Usage and availability -->
@DMAHP cites Cruickshank's (1947) discussion of using visuals as 'formal statistical assessment of the spatial pattern' as a major advancement.
@CD considers cartographic data analysis in practice. Presenting a clear guide for preparing cartograms for use with both qualitative and quantitative information.
The authors recognise that the creation of cartograms was largely the work of professional cartographers until the innovation of geographical information systems that welcomed map users as map creators. These systems are utilised depending on ‘the effectiveness, efficiency, and satisfaction of the map products (Nielsen 1994)’. @MACM also recognises the intuition that can be derived from choropleths must be 'validated by rigorous statistical analyses.'

@@

@@

@@

@@

@SAMGIS suggests it is the "investigators' objectives" that drive the "representation of diseases on maps". 
-infectious diseases may require choropleth methods

@@
